---
title: "Home Energy Visualisations by Council Area in Scotland 2020"
author: "Stephanie Duncan"
date: "26/03/2021"
output:
  pdf_document: default
  html_document: default
---

Initial data visualisations from home energy certifications by council area in Scotland for 2020.

Includes:

1. Mean CO2 Emissions Current Floor Area of Homes by Council Area - Annual CO2 equivalent emissions per square metre of floor area (units: kg.CO2e/m2/yr).

2. Mean Primary Energy Indicator - The amount of energy required at source, before conversion and transmission, to meet the calculated energy demand of the dwelling (Units: kWh/m2/year).

3. Mean Current Carbon Dioxide Emissions - The total annual emissions reduction for the building based upon the calculated energy demand for heating, cooling, lighting and ventilating the building. (Units: tonnes per year).


```{r include=FALSE}

library(shiny)
library(shinydashboard)
library(tidyverse)
library(sf)
library(here)
library(scales)
library(leaflet)
library(htmltools)
library(janitor)
```


```{r include=FALSE}
#Reading in cleaned file
home_energy_2020 <- read_csv(here("clean_data/home_energy_2020.csv"))
```


```{r include=FALSE}

#Table of the means per town for 2020
town_mean_2020 <- home_energy_2020 %>% 
  group_by(ca_name, quarter) %>% 
  summarise(mean_co2_emissions_current_per_floor_area_kg_co2_m_yr = round(mean(co2_emissions_current_per_floor_area_kg_co2_m_yr), digits = 2),
            mean_primary_energy_indicator_k_wh_m_year = round(mean(primary_energy_indicator_k_wh_m_year), digits = 2),
            mean_current_emissions_t_co2_yr = round(mean(current_emissions_t_co2_yr), digits = 2))
town_mean_2020
```

## 1. Mean CO2 Emissions Current Floor Area of Homes by Council Area


```{r include=FALSE}

mean_co2_emissions_current_per_floor_2020 <- town_mean_2020 %>% 
  group_by(ca_name) %>% 
  summarise(mean_co2_emissions_2020 = round(mean(mean_co2_emissions_current_per_floor_area_kg_co2_m_yr), digits = 2))

mean_co2_emissions_current_per_floor_2020

```

```{r echo=FALSE}
mean_co2_emissions_current_per_floor_2020 %>% 
  ggplot() +
  aes(x = mean_co2_emissions_2020, y = ca_name) +
  geom_col(fill = "dark green") +
  theme_minimal() +
  labs(
    y = "Council Area",
    x = "Mean CO2 Emissions Per Current Floor Area (kg CO2/m^2/Year)",
    title = "Mean CO2 Emissions Current Floor Area of Homes by Council Area",
    subtitle = "2020"
  ) +
  theme(axis.text.x = element_text(angle=45,hjust=1)) 

```

## 2. Mean Primary Energy Indicator of Homes by Council Area

```{r include=FALSE}

mean_primary_energy_indicator_2020 <- town_mean_2020 %>% 
  group_by(ca_name) %>% 
  summarise(mean_primary_2020 = round(mean(mean_primary_energy_indicator_k_wh_m_year), digits = 2))

mean_primary_energy_indicator_2020
```

```{r echo=FALSE}
mean_primary_energy_indicator_2020 %>% 
  ggplot() +
  aes(x = mean_primary_2020, y = ca_name) +
  geom_col(fill = "dark green") +
  theme_minimal() +
  labs(
    y = "Council Area",
    x = "Mean Primary Energy Indicator (kWh/m^2/yr)",
    title = "Mean Primary Energy Indicator of Homes by Council Area",
    subtitle = "2020"
  ) +
  theme(axis.text.x = element_text(angle=45,hjust=1)) 

```

## 3. Mean Current Carbon Dioxide Emissions

```{r include=FALSE}
mean_current_emissions_2020 <- town_mean_2020 %>% 
  group_by(ca_name) %>% 
  summarise(mean_current_emissions_2020 = round(mean(mean_current_emissions_t_co2_yr), digits = 2))

mean_current_emissions_2020
```


```{r echo=FALSE}
mean_current_emissions_2020 %>% 
  ggplot() +
  aes(x = mean_current_emissions_2020, y = ca_name) +
  geom_col(fill = "dark green") +
  theme_minimal() +
  labs(
    y = "Council Area",
    x = "Mean Current Emissions (Tonnes CO2/Year)",
    title = "Mean Current Emissions of Homes by Council Area",
    subtitle = "2020"
  ) +
  theme(axis.text.x = element_text(angle=45,hjust=1)) 
```

